%-------------------------
% Resume in LaTeX
% Author: Luke Wilson
% Tailored for Marvell Design/DSP/Verification Intern
%-------------------------

\documentclass[letterpaper,10pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\input{glyphtounicode}

\pagestyle{fancy}
\fancyhf{}
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.72in}
\addtolength{\textheight}{1.45in}

\urlstyle{same}
\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}
\setlist[itemize]{leftmargin=*, noitemsep, topsep=0pt, parsep=0pt, partopsep=0pt}

% Section formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-6pt}]

% PDF readable
\pdfgentounicode=1

% Custom commands
\newcommand{\resumeItem}[1]{\item \small{#1}}

\newcommand{\resumeSubheading}[4]{
  \vspace{-1pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small #3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-6pt}
}

\newcommand{\resumeProjectHeading}[2]{
  \vspace{-1pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{p{0.79\textwidth}@{\extracolsep{\fill}}r}
      \textbf{#1} & {\small #2} \\
    \end{tabular*}\vspace{-6pt}
}

\newcommand{\resumeItemListStart}{\begin{itemize}[leftmargin=0.18in]}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-7pt}}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}\vspace{-6pt}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{document}

%----------HEADING----------
\begin{center}
    \textbf{\Huge \scshape Luke Peter Wilson} \\ \vspace{2pt}
    \small San Diego, CA $|$
    \href{mailto:lukepeterwilson26@gmail.com}{\underline{lukepeterwilson26@gmail.com}} $|$
    \href{tel:+17608552996}{\underline{(760) 855-2996}} $|$
    \href{https://www.linkedin.com/in/luke-wilson-33718b238/}{\underline{linkedin.com/in/luke-wilson}} $|$
    \href{https://github.com/lukepwilson}{\underline{github.com/lukepwilson}}
\end{center}

%-----------EDUCATION-----------
\section{Education}
\resumeSubHeadingListStart
  \resumeSubheading
    {University of California, San Diego}{San Diego, CA}
    {Master of Science in Electrical Engineering}{Sept. 2025 -- Dec. 2026}
    \resumeItemListStart
      \resumeItem{\textbf{Coursework:} VLSI Algorithms \& Architectures; VLSI IC \& Systems Design; VLSI Advanced Topics; Digital Signal Processing; Information Theory \& Communications; Advanced Computer Architecture; Stochastic Modeling.}
    \resumeItemListEnd

  \resumeSubheading
    {University of California, San Diego}{San Diego, CA}
    {Bachelor of Science in Electrical Engineering, GPA: 3.704}{Sept. 2021 -- June 2025}
    \resumeItemListStart
      \resumeItem{\textbf{Coursework:} VLSI Digital Circuits \& Systems; Communication Systems; Digital Signal \& Image Processing; Probability \& Random Processes; Linear Electronic Circuits; Electromagnetism; Object-Oriented Programming; Deep Learning; Linear Control Theory.}
    \resumeItemListEnd
\resumeSubHeadingListEnd

%-----------TECHNICAL SKILLS-----------
\section{Technical Skills}
\begin{itemize}[leftmargin=0.15in, label={}]
  \small{\item{
    \textbf{Programming:} Python, SystemVerilog/Verilog, C/C++, MATLAB, Bash, ARM Assembly \\
    \textbf{RTL Design \& Verification:} RTL design, SystemVerilog testbenches, UVM basics, constrained-random testing, functional verification, hardware debugging, waveform analysis, code/functional coverage, pre-silicon verification \\
    \textbf{EDA \& Simulation:} Synopsys Design Compiler, Cadence Innovus, Cadence Virtuoso, ModelSim/QuestaSim, Intel Quartus Prime, Xilinx Vivado, LTspice/PSpice \\
    \textbf{ASIC / Digital Design:} Synthesis, lint, gate-level simulation, STA (setup/hold timing, WNS/TNS), SDC constraints, CDC analysis, pipeline design, RTL integration and bring-up \\
    \textbf{DSP \& Communications:} OFDM, MIMO, channel estimation, equalization, digital signal processing, wireless systems \\
    \textbf{Hardware \& Instruments:} Ettus USRP B210/X410, PlutoSDR, FPGA prototyping, oscilloscopes, spectrum analyzers, signal generators
  }}
\end{itemize}

%-----------PROJECTS-----------
\section{Projects}
\resumeSubHeadingListStart

  \resumeProjectHeading
    {Dual-Core Machine Learning Accelerator for Attention Mechanisms \emph{| Verilog, SystemVerilog, Innovus, ModelSim}}{2026--Present}
    \resumeItemListStart
      \resumeItem{Designed RTL for a dual-core systolic-array accelerator implementing the $Q \cdot K^{T}$ attention operation and normalization pipeline.}
      \resumeItem{Implemented a full RTL-to-GDSII flow including synthesis, timing constraint development, lint-style checks, and place-and-route while targeting 1 GHz timing closure.}
      \resumeItem{Developed SystemVerilog testbenches and debugged functional issues through simulation and waveform analysis across hierarchical modules.}
      \resumeItem{Integrated custom SRAM blocks and optimized datapath pipelines for timing, area, and power efficiency.}
    \resumeItemListEnd

  \resumeProjectHeading
    {Near-Field MIMO Approach for Ground Stations \emph{| MATLAB, Python, OFDM, MIMO, USRP}}{2025}
    \resumeItemListStart
      \resumeItem{Built a $2\times2$ mmWave MIMO hardware testbed to extract CSI and characterize high-speed wireless link performance.}
      \resumeItem{Developed Python and MATLAB test pipelines to automate data collection, execute functional experiments, and debug channel estimation and equalization behavior.}
      \resumeItem{Integrated SDR hardware with software processing pipelines, enabling rapid system bring-up and measurement-driven analysis of OFDM links.}
      \resumeItem{Co-authored paper accepted at IEEE INFOCOM 2026.}
    \resumeItemListEnd

  \resumeProjectHeading
    {Kogge-Stone Adder \emph{| Cadence Virtuoso, CMOS Logic, Dynamic Logic}}{2025}
    \resumeItemListStart
      \resumeItem{Designed and simulated an 8-bit Kogge-Stone adder in Cadence Virtuoso using static CMOS and dynamic logic styles.}
      \resumeItem{Analyzed critical-path timing and optimized transistor-level implementations, achieving 3.1 GHz operation in the complementary logic design.}
      \resumeItem{Debugged signal propagation delays and evaluated speed--power trade-offs across multiple logic implementations under design constraints.}
    \resumeItemListEnd

\resumeSubHeadingListEnd

%-----------EXPERIENCE-----------
\section{Experience}
\resumeSubHeadingListStart

  \resumeSubheading
    {Research Volunteer, WCSNG @ UCSD}{June 2024 -- Present}
    {University of California, San Diego}{La Jolla, CA}
    \resumeItemListStart
      \resumeItem{Developed Python/MATLAB simulation tools and hardware test pipelines to debug OFDM transceiver behavior and wireless channel estimation algorithms.}
      \resumeItem{Integrated software processing pipelines with USRP-based hardware platforms to collect, validate, and analyze experimental link data.}
      \resumeItem{Collaborated with PhD students on cross-functional experiments spanning DSP algorithms, RF measurements, and system-level performance evaluation.}
    \resumeItemListEnd

  \resumeSubheading
    {Teaching Assistant, ECE Department}{Sept. 2025 -- Dec. 2025}
    {University of California, San Diego}{La Jolla, CA}
    \resumeItemListStart
      \resumeItem{Taught Electromagnetism concepts including transmission lines, Maxwell's equations, and wave propagation; hosted office hours and graded assignments.}
    \resumeItemListEnd

\resumeSubHeadingListEnd

%-----------ADDITIONAL INFORMATION-----------
\section{Extra Information}
\begin{itemize}[leftmargin=0.15in, label={}]
  \small{\item{
    \textbf{Achievements:} Valedictorian of high school, 99th Percentile SAT, \href{https://www.ece.ucsd.edu/undergraduate/booker-award}{\underline{Booker Award Recipient}}, Proficient in German.
  }}
\end{itemize}

%-------------------------------------------
\end{document}