%-------------------------
% Resume in LaTeX
% Author: Luke Wilson
% Tailored version for NVIDIA Digital Circuit Design Internship
%-------------------------

\documentclass[letterpaper,10pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\input{glyphtounicode}

\pagestyle{fancy}
\fancyhf{}
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.72in}
\addtolength{\textheight}{1.45in}

\urlstyle{same}
\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}
\setlist[itemize]{leftmargin=*, itemsep=0pt, topsep=1pt, parsep=0pt, partopsep=0pt}

\titleformat{\section}{
  \vspace{2pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-3pt}]

\pdfgentounicode=1

\newcommand{\resumeItem}[1]{\item \small{#1}}

\newcommand{\resumeSubheading}[4]{
  \vspace{1pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small #3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-1pt}
}

\newcommand{\resumeProjectHeading}[2]{
  \vspace{1pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{p{0.78\textwidth}@{\extracolsep{\fill}}r}
      \textbf{#1} & {\small #2} \\
    \end{tabular*}\vspace{-1pt}
}

\newcommand{\resumeItemListStart}{\begin{itemize}[leftmargin=0.18in, itemsep=0pt, topsep=1pt]}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-2pt}}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}\vspace{-1pt}}

\begin{document}

\begin{center}
    \textbf{\Huge \scshape Luke Peter Wilson} \\ \vspace{2pt}
    \small San Diego, CA $|$
    \href{mailto:lukepeterwilson26@gmail.com}{\underline{lukepeterwilson26@gmail.com}} $|$
    \href{tel:+17608552996}{\underline{(760) 855-2996}} $|$
    \href{https://www.linkedin.com/in/luke-wilson-33718b238/}{\underline{linkedin.com/in/luke-wilson}}
\end{center}

\section{Education}
\resumeSubHeadingListStart
  \resumeSubheading
    {University of California, San Diego}{San Diego, CA}
    {Master of Science in Electrical Engineering}{Sept. 2025 -- Dec. 2026}
    \resumeItemListStart
      \resumeItem{\textbf{Coursework:} VLSI Algorithms \& Architectures; VLSI IC \& Systems Design; Advanced Computer Architecture; Digital Signal Processing; Stochastic Modeling.}
    \resumeItemListEnd

  \resumeSubheading
    {University of California, San Diego}{San Diego, CA}
    {Bachelor of Science in Electrical Engineering, GPA: 3.704}{Sept. 2021 -- June 2025}
    \resumeItemListStart
      \resumeItem{\textbf{Coursework:} VLSI Digital Circuits \& Systems; Digital Signal \& Image Processing; Probability \& Random Processes; Communication Systems; Object-Oriented Programming; Electromagnetism.}
    \resumeItemListEnd
\resumeSubHeadingListEnd

\section{Technical Skills}
\begin{itemize}[leftmargin=0.15in, label={}]
  \small{\item{
    \textbf{Languages:} Verilog, SystemVerilog, Python, C/C++, MATLAB, Bash, ARM Assembly \\
    \textbf{Digital Circuit Design:} RTL design, datapath design, pipelining, register-transfer level verification, functional debug, waveform analysis, gate-level simulation, CMOS logic \\
    \textbf{ASIC Flow \& Tools:} Cadence Innovus, Synopsys Design Compiler, Cadence Virtuoso, ModelSim/QuestaSim, Quartus Prime, Vivado, STA, synthesis, place-and-route \\
    \textbf{Design Topics:} Register files, math-intensive datapaths, timing closure, power/area optimization, CDC basics, SDC constraints \\
    \textbf{Hardware \& Simulation:} FPGA prototyping, LTspice/PSpice, oscilloscopes, spectrum analyzers, function generators
  }}
\end{itemize}

\section{Projects}
\resumeSubHeadingListStart

  \resumeProjectHeading
    {Dual-Core ML ASIC Accelerator \emph{| Verilog, SystemVerilog, Innovus, ModelSim}}{2026--Present}
    \resumeItemListStart
      \resumeItem{Designed RTL for a dual-core systolic-array accelerator implementing the $Q \cdot K^{T}$ attention operation and normalization datapath.}
      \resumeItem{Built and verified math-intensive digital logic with SystemVerilog testbenches, waveform analysis, and gate-level validation across hierarchical modules.}
      \resumeItem{Implemented synthesis and place-and-route flow, developed timing constraints, and optimized pipelines for timing, power, and area.}
    \resumeItemListEnd

  \resumeProjectHeading
    {Kogge-Stone Adder \emph{| Cadence Virtuoso, CMOS Logic, Dynamic Logic}}{2025}
    \resumeItemListStart
      \resumeItem{Designed and simulated an 8-bit high-speed adder in Cadence Virtuoso using static CMOS and dynamic logic techniques.}
      \resumeItem{Analyzed critical-path timing and optimized transistor-level implementations, achieving 3.1 GHz operation in the complementary logic design.}
      \resumeItem{Strengthened digital circuit fundamentals through delay balancing, buffering, and high-performance datapath optimization.}
    \resumeItemListEnd

  \resumeProjectHeading
    {Near-Field MIMO Ground Station \emph{| MATLAB, Python, OFDM, MIMO, USRP}}{2025}
    \resumeItemListStart
      \resumeItem{Built a $2\times2$ mmWave MIMO hardware testbed and automated experiments with Python and MATLAB for repeatable validation.}
      \resumeItem{Integrated hardware and software pipelines to collect data, validate behavior, and troubleshoot system-level implementation issues.}
    \resumeItemListEnd

\resumeSubHeadingListEnd

\section{Experience}
\resumeSubHeadingListStart

  \resumeSubheading
    {Research Volunteer, WCSNG @ UCSD}{June 2024 -- Present}
    {University of California, San Diego}{La Jolla, CA}
    \resumeItemListStart
      \resumeItem{Developed Python/MATLAB tools to support simulation, hardware validation, and measurement analysis for wireless systems research.}
      \resumeItem{Collaborated with PhD students to debug implementation issues, analyze results, and improve experimental workflows across cross-functional tasks.}
    \resumeItemListEnd

  \resumeSubheading
    {Teaching Assistant, ECE Department}{Sept. 2025 -- Dec. 2025}
    {University of California, San Diego}{La Jolla, CA}
    \resumeItemListStart
      \resumeItem{Supported Electromagnetism instruction through office hours, grading, and technical problem-solving guidance.}
    \resumeItemListEnd

\resumeSubHeadingListEnd

\vspace{-8pt}
\section{Extra Information}
\begin{itemize}[leftmargin=0.15in, label={}]
  \small{\item{
    \textbf{Achievements:} \href{https://www.ece.ucsd.edu/undergraduate/booker-award}{\underline{Booker Award Recipient}}, Valedictorian, 99th Percentile SAT, Proficient in German.
  }}
\end{itemize}

\end{document}
